Attributions for Poverty in Post-Socialist Countries

### 2014-02-11 article2013.Rmd

```{rattribArticleDescTbl1, results='asis', eval=TRUE, echo=FALSE, cache=TRUE, message=FALSE}
source("code/dv_tables.R")
library(xtable)
print.xtable(xtable(tbl5,digits=1,
                    caption="Weighted population shares of dependent variable by country",), #table.placement="H",
             type="latex",
             comment=FALSE, 
             include.rownames=FALSE,
             caption.placement="top",
             size="scriptsize")
```

@@

@@

@@

Lepianka, Dorota and Gelissen, John and van Oorschot, Wim (2010) Popular Explanations of Poverty in Europe. E

>>>>

```{rattribArticleDescTbl1, results='asis', eval=TRUE, echo=FALSE, cache=TRUE, message=FALSE}
source("code/dv_tables.R")
library(xtable)
print.xtable(xtable(tbl5,digits=1,
                    caption="Weighted population shares of dependent variable by country",), #table.placement="H",
             type="latex",
             comment=FALSE, 
             include.rownames=FALSE,
             caption.placement="top",
             size="scriptsize")

@@

=======

@@

>>>>>>> gh-pages

@@

Lepianka, Dorota and Gelissen, John and van Oorschot, Wim (2010) Popular Explanations of Poverty in Europe. Effects of Contextual and Individual Characteristics across 28 European Countries. Acta Sociologica 53 (1), 53–72.

Morçöl, Göktuğ (1997) Lay Explanations for Poverty in Turkey and Their Determinants. Journal of Social Psychology 137 (6) 728–738.

Murthi, M., & Tiongson, E. R. (2008). Attitudes to Equality: The Socialist Legacy Revisited. SSRN eLibrary. Retrieved from http://papers.ssrn.com/sol3/papers.cfm?abstract_id=1098627

Nasser, Ramzi and Abouchedid, Kamal and Khashan, Hilal (2002) Perceptions of the Causes of Poverty Comparing Three National Groups: Lebanon, Portugal, and South Africa. Current Research in Social Psychology 8 (7), 101–119.

Niemelä, Mikko (2008) Perceptions of the Causes of Poverty in Finland. Acta Sociologica, 51 (1), 23–40.

Nilson, Lina B. (1981) Reconsidering Ideological Lines: Beliefs about Poverty in America. The Sociological Quarterly 22 (4), 531-548.

Ragin, Charles C. (1987) The Comparative Method. Moving Beyond Qualitative and Quantitative Strategies. Berkeley: University of California Press.

Rothstein, Bo (2000) Trust, Social Dilemmas and Collective Memories. Journal of Theoretical Politics, 12 (4), 477–501.

Rothstein, Bo and Stolle, Dietlind (2008) The State and Social Capital: An Institutional Theory of Generalized Trust. Comparative Politics 40 (4), 441-459.

Saunders, Peter (2002) The Ends and Means of Welfare. Coping with Economic and Social Change in Australia. Cambridge: Cambridge University Press.

Schumpeter, Joseph A. (1942) Capitalism, Socialism & Democracy. New York: Harper & Brothers.

Szikra, D., & Tomka, B. (2009). Social Policy in East Central Europe: Major Trends in the Twentieht Century. In Post-communist Welfare Pathways (Vol. 2009).

Stephenson, Svetlana (2000) Public Beliefs in the Causes of Wealth and Poverty and Legitimization of Inequalities in Russia and Estonia. Social Justice Research 13 (2), 83–100.

Svallfors, Stefan (1997) Worlds of Welfare and Attitudes to Redistribution: A Comparison of Eight Western Nations. European Sociological Review 13 (3), 283–304.

Tomka, B. (2006). East Central Europe and the European Social Policy Model: A Long-Term View. East European Quarterly, 40(2), 135.

van Oorschot, Wim and Halman, Loek (2000) Blame or Fate, Individual or Social? An International Comparison of Popular Explanations of Poverty. European Societies 2 (1), 1–28.

Wilson, George (1996) Toward a Revised Framework for Examining Beliefs about the Causes of Poverty. The Sociological Quarterly 37 (3), 413–428.
